Active Learning from Blackbox to Timed Connectors

### 2016-01-11 paper/paper.tex
.

\usepackage{amssymb}
\usepackage{cite}
\usepackage[normalem]{ulem}
% for a smile-face character
\usepackage{wasysym}
% listing for codes
\usepackage{listings}

@@

@@

\subsection{Reo Coordination Language}
\label{sec:reo}
Reo is a channel based exogenous coordination language proposed by F. Arbab. in
\cite{DBLP:journals/mscs/Arbab04}. A Reo model, also called \emph{connector}, provides the protocol
that formalizes the communication, synchronization and cooperation among the components which
communicate through the connector. Connectors can be defined with no knowledge of the components,
which makes Reo a powerful ``glue language'' in component-based
development\cite{DBLP:journals/sigsoft/Gill03}.

In Reo, complex connectors are made up of simpler ones, where the atomic connectors are called
\emph{channels}. Each channel has two \emph{channel ends}. There are two type of channel ends:
\emph{source} and \emph{sink}. Source channel ends accepts data into the channel, while sink
channels ends release them out of the channel. Channels are attached on component instances
or \emph{nodes}.

@@

\begin{itemize}
  \item [-] A \emph{Sync} channel accepts a data item from its source end iff. the data item can be
    dispensed to its sink end simultaneously.
  \item [-] A \emph{LossySync} channel is always prepared to accept data items. These items will be
    send to its sink end simutaneously if possible, otherwise they will be dropped.
  \item [-] A \emph{SyncDrain} channel has two source ends and no sink end. It can accept a data
    item through one of its source end iff. a data item is also available for it to simultaneously
    accept through the other end. Then both two data items will be lost.
  \item [-] 
\end{itemize}

@@

\todo{do we need to remove this graph?}
\begin{figure}[h]
  \begin{center}
    \input{./images/reoextend.tex}
  \end{center}
  \caption{Merger and Replicator}
  \label{fig:reoextend}
\end{figure}

@@

\todo{modify the listings package}
\begin{lstlisting}
int main(int argc, char ** argv)
{
  printf(``Hello world!n'');
  return 0;
}
\end{lstlisting}

>>>>

\usepackage{amssymb}
\usepackage{cite}
\usepackage[normalem]{ulem}
% for a smile-face character
\usepackage{wasysym}
% listing for codes
\usepackage{listings}
% listing for golang
% NOTE listings-golang.sty is required
\usepackage{listings-golang}

@@

% style of source code environment listings
\lstset{basicstyle=\footnotesize\ttfamily,breaklines=true}
\lstset{framextopmargin=50pt,frame=bottomline, language=Golang}

@@

\subsection{Reo Coordination Language}
\label{sec:reo}
We provide here a brief overview of the main concepts of Reo, more details can be found in
\cite{DBLP:journals/mscs/Arbab04, DBLP:journals/scp/BaierSAR06}.

Reo is a channel based exogenous coordination language proposed by F. Arbab. 
A Reo model, also called \emph{connector}, provides the protocol
that formalizes the communication, synchronization and cooperation among the components which
communicate through the connector. Connectors can be defined with no knowledge of the components,
which makes Reo a powerful ``glue language'' in component-based
development\cite{DBLP:journals/sigsoft/Gill03}.

In Reo, complex connectors are made up of simpler ones, where the atomic connectors are called
\emph{channels}. Each channel has two \emph{channel ends}. There are two type of channel ends:
\emph{source} and \emph{sink}. Source channel ends accepts data into the channel, while sink
channels ends release them out of the channel.

@@

\begin{itemize}
  \item [-] A \emph{Sync} channel accepts a data item from its source end iff. the data item can be
    dispensed to its sink end simultaneously.
  \item [-] A \emph{LossySync} channel is always prepared to accept data items. These items will be
    send to its sink end simutaneously if possible, otherwise they will be dropped.
  \item [-] A \emph{SyncDrain} channel has two source ends and no sink end. It can accept a data
    item through one of its source end iff. a data item is also available for it to simultaneously
    accept through the other end. Then both two data items will be lost.
  \item [-] A A \emph{FIFO1} channel is an asychronous channel with one buffer cell. It accepts a
    data item whenever the buffer is empty.  
\end{itemize}

@@

Channels are attached on component instances or \emph{nodes}. There are three types of nodes:
\emph{source}, \emph{sink} and \emph{mixed node}, depending on whether all channel ends that
coincide on a node are source ends, sink ends or both. (see in Figure \ref{fig:node})

\begin{figure}[h]
  \begin{center}
    \input{./images/nodes.tex}
  \end{center}
  \caption{Source, Sink and Mixed Nodes in Reo}
  \label{fig:node}
\end{figure}

With definition of more basic channels, it's easy to extend Reo to formalize coordination in
different areas. In this paper, we take timed Reo\cite{DBLP:conf/sefm/ArbabBBR04} as our formal
model. Timed Reo includes several timed channels, where the most commonly-used one, called
\emph{timer}, is also shown in Figure \ref{fig:basic}. A t-timer channel accepts any data item from
its source end and returns on its sink end a timeout signal after a delay of t time units.

Components can be linked to source nodes or sink nodes. A component can write data items to its
corresponding source node only if the data item can be dispensed simultaneously to all source ends
on this node. Meanwhile, a component can read a data item only if there is at least one readable
sink end on its corresponding node. A mixed node non-determinstically selects and takes a data item
from one of its coincident sink channel ends and replicates it into all of its coincident source
channel ends.

\begin{figure}[h]
  \begin{center}
    \input{./images/connectorexample.tex}
  \end{center}
  \caption{Coordination with Reo Connectors}
  \label{fig:reoconnector}
\end{figure}

As shown in Figure \ref{fig:reoconnector}, we use a simple example to illustrate how complex
connectors are constructed and used in coordination. In this example, COM1,COM2 and
MONITOR are components. With an \emph{alternator} connector, MONITOR can receive data items from
COM1 and COM2 alternately.

@@

\begin{lstlisting}
int main(int argc, char ** argv)
{
  printf(``Hello world!n'');
  return 0;
}
\end{lstlisting}
